Composable Generalized Consensus

### 2015-05-15 paper/intro.tex
Work on the intro, emphasis on the two intermediate specs.

The key novelty of our framework lies in its practical applicability, allowing
the execution of commutative commands without synchronization and reducing the
replication overhead from $2*k+1$ replicas to $k+1$ replicas, to tolerate $k$
replica crashes, using a reliable external reconfiguration master.

>>>>

The key novelty of our framework lies in its practical applicability.
Most SMR algorithms are variations on a basic structure consisting of one of two kinds of 
quorum systems \cite{GuerraouiVukolic10RefinedQuorumSystems}. 
The first kind, that we call resilient quorums, are used in leader-based algorithms, while the second
kind of quorums, that we call fast quorums, are used in leader-less algorithms and can order commuting commands without synchronization.
We provide two specifications, at an intermediate level of abstraction, that capture the essence of composing algorithms using these two kinds of quorums.
Our two specifications allow to easily check that new modules based on resilient or fast quorums are correct, covering a large spectrum of practical algorithms.
